---
title: "Pre-Analysis Data Cleaning"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(bipartite)
library(readxl)
library(knitr)
library(magrittr)

FullData<- read_csv('../Data/SimplifiedFullData.csv') 
```

# Introduction

This script converts the raw host and parasitoid data into different types of network. It also carries out bootstrapping of the whole procedure to generate an ensemble of re-drawn quantitative networks.

# Reading in data

```{r message=FALSE, warning=FALSE, echo = FALSE}
FullData<- read_csv('../Data/SimplifiedFullData.csv') 
ParaNiceNames <- read_csv('../Data/ParaNames2.csv') # various aliases for each species.
stopifnot(unique(FullData$Parasitoid) %in% ParaNiceNames$Parasitoid) # Check that all names are included

left_join(FullData, ParaNiceNames, by ='Parasitoid') -> FullData

Iffy <- c('Unparasitised','Unidentified',
          'not blasted', 'not blasted (beetle)',
          'tissue contamination',
          'tissue contamination (beetle)',
          'unidentified' )
```

# Relative Host Abundances
Note that not all the parasitism ID was successful:
```{r echo = FALSE}
RelHostData<- filter(FullData,
                     Core == 'yes',
                     !is.na(Host) )  # filter out the unidentified ones 
```

```{r echo = FALSE}
P_summ_Rel<- RelHostData%>%
  count(Site, P_summary )%>%
  spread(P_summary, n)%>%
  set_colnames(c('Site', 'Parasitised', 'Not-Parasitised'))

Both_av_Rel<- RelHostData%>%
  count(Site, BothAvailable )%>%
  spread(BothAvailable, n)%>%
  set_colnames(c('Site', 'ID Available', 'ID Not Available'))%>%
  mutate(Total = `ID Available`+`ID Not Available`)

full_join(P_summ_Rel, Both_av_Rel, by = "Site")%>%
  kable(caption = 'Core Network Counts')
```

# Enriching interactions

```{r echo = FALSE}
FullData%>%
  filter(extracted == 'yes')%>%  # 6780 records
  filter( Site %in% c('K070','K390','K730' , 
                      'P070','P350','P880') ) %>%  # 3,740 records
  filter(is.na(Core))-> EnrichingData # This is  2659 records (as per email)
```

```{r echo = FALSE}  
P_sum_enrich<-  EnrichingData  %>%
  count(Site,  P_summary) %>% 
  spread(P_summary, n)%>%
  set_colnames(c('Site', 'Parasitised', 'Not-Parasitised')) # 409 of these were parasitised

Both_av_enrich<- FullData %>%
  filter(extracted == 'yes',
         Site %in% c('K070','K390','K730' , 'P070','P350','P880'),
         is.na(Core))%>%
  count(Site, BothAvailable )%>%
  spread(BothAvailable, n)%>%
  set_colnames(c('Site', 'ID Available', 'ID Not Available'))%>%
  mutate(Total = `ID Available`+`ID Not Available`)

full_join(P_sum_enrich, Both_av_enrich, by = "Site")%>%
  kable(caption = 'Enriched Network Counts')
```

```{r echo = FALSE}
### Additional host and parasitoid data (the complex, enriched part)
FullData %>%
   filter(!is.na(extracted),
          !is.na(Host))%>% 
  count(Core,Site)%>%
  spread(Core, n) %>%
  rename(Core = yes,
         Enriching = `<NA>`)%>%
  kable(caption = 'Variable amount of enriching between sites.')
```

# Site-level frequency of host

```{r  echo = FALSE}
RelHostData %>%
  count(Site, Host) %>%
  spread(Host, n, fill = 0) -> HostCountTable

HostCountTable%>%
  column_to_rownames('Site')%>%
  t()%>%
  kable(caption = 'Host counts in core networks used to determine relative host frequencies')

HostTotals<- matrix(rowSums(HostCountTable[,-1]),
                    nrow=6, ncol = ncol(HostCountTable)-1)

HostFreqTable<- HostCountTable[,-1] / HostTotals
```

# Site and Host Level Parasitism Rate

```{r echo = FALSE}
RelHostData %>%
  mutate(P_summary = ifelse(is.na(P_summary),'no', 'yes' )) %>%
  count(Site, Host, P_summary) %>%
  spread(P_summary, n, fill = 0) %>%
  mutate(FracPara = yes/(no+yes)) -> SiteHostRateData

count(SiteHostRateData, yes )%>% # NB 
  kable(caption = 'Table of frequencies of number of observed interactions per host species, per site. Most counts are pretty small, so there is likely to be a lot of noise and uncertainity')

SiteHostRateData%>%
  select(-no, -yes)%>%
  spread(Host, FracPara, fill = 0) -> HostParaRateTable

HostParaRateTable%>%
  column_to_rownames('Site')%>%
  t()%>%
  kable(caption = 'Host:Site Parasitism Rates used to calculate quantitive interaction network.',
        digits = 3)
```

# Relative frequency of Host-wasp interactions

```{r echo = FALSE}
FullData %>%
  filter(!is.na(extracted),
         Site %in% c('K070'  ,'K390','K730','P070','P350','P880'),
         !is.na(Host),
         !is.na(Parasitoid))%>%
  mutate(Unusable = Parasitoid %in%  Iffy|Host =='sulfurigaster complex') %>%# Still getting `sulfurigaster complex` showing up. Removed as just one and indeterminate
  filter(!Unusable) %>%
  select(Site, Host, ShortParaName)-> RelativeIntsData

RelativeIntsData%>%
  count(Site,Host, name = 'Total') -> TotalsPerSite

RelativeIntsData %>%
  count(   Site,Host,ShortParaName  ) %>%
  left_join(TotalsPerSite, by = c("Site", 'Host')) %>%
  mutate(RelFreq = n/Total) -> RelIntFreqData

```

# Creating Enriched Network

At each site assume 1000 observed hosts.

```{r echo = FALSE}
AttackedHosts <- HostFreqTable  * HostParaRateTable[,-1] *1000

AttackedHosts$Site <- c('K070'  ,'K390','K730','P070','P350','P880')

AttackedHosts%>%
  gather('Host', 'Attacked', bipectinata:sulfurigaster) %>%
  full_join(RelIntFreqData, by = c('Site', 'Host'))%>%
  filter(!is.na(n))%>%
  mutate(est_N_ints_per1000 = Attacked * RelFreq) -> EnrichedInteractionList1000

EnrichedInteractionList1000 %>%
  filter(Site == 'K070') %>%
  kable(caption = 'Example quantitative interaction network for K070.',
        digits = 3)
```

```{r}

save(RelHostData, file = '../GeneratedData/RelHostData') 
save(FullData, file = '../GeneratedData/FullData') 
save(EnrichedInteractionList1000, file = '../GeneratedData/EnrichedInteractionList1000') 
```

# Bootstrapping enriched networks


```{r}

# Relative Host Abundances
RelHostData<- filter(FullData,
                     Core == 'yes',
                     !is.na(Host) )  # filter out the unidentified ones (i.e. the blanks?)

RelHostData %>%
  count(Site, Host) %>%
  spread(Host, n, fill = 0) -> HostCountTable
RelHostData %>%
  mutate(P_summary = ifelse(is.na(P_summary),'no', 'yes' )) %>%
  count(Site, Host, P_summary) %>%
  spread(P_summary, n, fill = 0) -> HostSiteParaObs


# Relative frequency of each Host-wasp interaction
RelativeIntsData<- FullData %>%
  filter(!is.na(extracted),
         Site %in% c('K070'  ,'K390','K730','P070','P350','P880'),
         !is.na(Host),
         !is.na(Parasitoid))%>%
  mutate(Unusable = Parasitoid %in%  Iffy|Host =='sulfurigaster complex') %>%# Still getting `sulfurigaster complex` showing up. Removed as just one and indeterminate
  filter(!Unusable) %>%
  select(Site, Host, ShortParaName)

RelativeIntsData%>%
  count(Site,Host, name = 'Total') -> HostTotalsPerSite
RelativeIntsData %>%
  count(   Site,Host,ShortParaName  )%>% 
  spread(ShortParaName , n, fill = 0) -> InteractionTotalsPerSite

```

### Define Bootstrapping function

```{r}
BootstrapAndEnrich <- function(seed, HostCountTable, HostSiteParaObs, HostTotalsPerSite, InteractionTotalsPerSite){
  
  set.seed(seed)
  
  #######################
  ## Resampling counts here
  
  ## Host counts
  NewHostCountTable <- HostCountTable
  
  for(i in 1: nrow(HostCountTable)){
    NewHostCountTable[i,-1]<- rmultinom(1, sum(HostCountTable[i,-1]),   HostCountTable[i,-1])
  }
  
  ## Resampling Host Parasitism observations for parasitism rate 
  # NB many of these are totally one or the other, so not a great estimation... But not much to build a proper Bayesian model out of either 
  
  HostSiteParaObs$RedrawnNo <- NA
  HostSiteParaObs$RedrawnYes <-NA
  
  for(i in 1: nrow(HostSiteParaObs)){
    
    Draw_xxx<- rmultinom(1, HostSiteParaObs$no[i] + HostSiteParaObs$yes[i],
                         c( HostSiteParaObs$no[i] , 
                            HostSiteParaObs$yes[i]))
    HostSiteParaObs$RedrawnNo[i]<-  Draw_xxx[1]
    HostSiteParaObs$RedrawnYes[i]<-  Draw_xxx[2]
  }
  
  ### Redrawning parasitoids that attacked each host at each site. Again, minimal style and no cross-drawing. 
  NewInteractionTotalsPerSite <- InteractionTotalsPerSite 
  NP<- ncol(InteractionTotalsPerSite)
  
  for(i in 1: nrow(InteractionTotalsPerSite)){
    NewInteractionTotalsPerSite[i,3:NP ] <- rmultinom(1, sum(InteractionTotalsPerSite[i, 3:NP]),
                                                      InteractionTotalsPerSite[i, 3:NP])
  }
  
  
  ##################
  #### Returning to long format, joining and calculating frequencies:
  
  
  NewInteractionTotalsPerSite %>% 
    gather('ShortParaName', 'n', -Site, -Host) %>%
    left_join( HostTotalsPerSite,      # This host totals is just used for calculating paratistism frequency, so it is not redrawn. 
               by = c("Site", 'Host')) %>%
    mutate(RelFreq = n/Total) -> RelIntFreqData
  
  HostSiteParaObs%>%
    mutate(FracPara = RedrawnYes/(RedrawnNo+RedrawnYes))%>%
    select(-no,-RedrawnNo,  -yes, -RedrawnYes)%>%
    spread(Host, FracPara, fill = 0) -> HostParaRateTable
  
  
  HostTotals<- matrix(rowSums(HostCountTable[,-1]),
                    nrow=6, ncol = ncol(HostCountTable)-1)
  HostFreqTable<- NewHostCountTable[,-1] / HostTotals

  
  # Creating Enriched Network 
  AttackedHosts <- HostFreqTable  * HostParaRateTable[,-1] *1000
  AttackedHosts$Site <- c('K070'  ,'K390','K730','P070','P350','P880')
  AttackedHosts%>%
    gather('Host', 'Attacked', bipectinata:sulfurigaster) %>%
    full_join(RelIntFreqData, by = c('Site', 'Host'))%>%
    filter(!is.na(n))%>%
    mutate(est_N_ints_per1000 = Attacked * RelFreq)%>%
    filter(est_N_ints_per1000 >0)-> EnrichedInteractionList
  
  
  return(EnrichedInteractionList)
}
```

Take 1000 bootstraps and save:

```{r eval = FALSE}
ListOfBootstrapDraws<-map(1:1000, BootstrapAndEnrich, HostCountTable, HostSiteParaObs, HostTotalsPerSite, InteractionTotalsPerSite)
save(ListOfBootstrapDraws, file = '../GeneratedData/ListOfBootstrapDraws')


ListOfBootstrapDraws[[1]]%>%
  filter(Site == 'K070')

EnrichedInteractionList1000%>%
  filter(Site == 'K070')

```

```{r eval = FALSE}
load('../GeneratedData/ListOfBootstrapDraws')


InteractionList <- ListOfBootstrapDraws[[1]]


MeasureBootstrapping<-function(InteractionList){
  
  InteractionList%>%
    frame2webs( c('Host', 'ShortParaName', 'Site', 'est_N_ints_per1000'),
                emptylist = TRUE)-> Networks
  
  Networks %>%
    map_df(networklevel,
           H2_integer=FALSE,
           index =  c('H2', "weighted NODF"))%>%
    t%>%
    as.data.frame()%>%
    rownames_to_column() %>%
    magrittr::set_colnames( c('Site',"weighted NODF", 'H2' )) -> Metrics
  
  Metrics$Modularity<- map(Networks,  safely(function(x){metaComputeModules(x)@likelihood}, otherwise = NA))%>%map_dbl('result')
  return(Metrics)
}


Quant_MeasuresOverBootstraps<- map_df(ListOfBootstrapDraws, MeasureBootstrapping)
save(Quant_MeasuresOverBootstraps, file= '../GeneratedData/Quant_MeasuresOverBootstraps')

```

# Tidy Data For Deposition

```{r}
FullData%>%
  filter(extracted=='yes')%>%
  filter(Host != 'sulfurigaster complex' | is.na(Host))%>%
  mutate(Parasitised = ifelse(!is.na(P_summary), TRUE, FALSE),
         ExposureLength = recode(ExposureLength,
                                 `10.1`  = 'short',
                                 `10.2` = 'medium',
                                 `20` = 'long'    ),
         Group = ifelse(!is.na(Core), 'Core', 
                        ifelse(is.na(Core)& !is.na(BothAvailable),'Enriching',
                               ifelse(is.na(Host), 'Screen Only', 'Enriching' ))))%>% 
  select(-extracted, -n, -P_summary, -ReplacemeSequencet, - ParaName, 
         - BothAvailable, -Parasitoid, - ShortParaName, - Core)%>%
  rename(Parasitoid = LongName)%>%
  arrange(SampleID)-> DataForNERC

DataForNERC %>%
  count(Site, TrapID)


kable(head(DataForNERC))

# write_csv(DataForNERC, '../Data/PupaeIdentification.csv')
```

# Session Info

```{r}
sessionInfo()
```